---
title: "JFS Neighborhood-Level Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: kable
params: 
  d: d
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(knitr)
library(tmap)
tmap_mode('view')
```

```{r}
d <- params$d
# d <- read_csv('test/simulated_jfs_data_geocoded.csv.csv',
#                             col_types = cols(INTAKE_ID = col_character(),
#                                PERSON_ID = col_character(),
#                                REPORTER_PERSON_ID = col_character(),
#                                PROVIDER_ID = col_character(),
#                                fips_tract_id = col_character()))
```

# Overall Summary

```{r}
date_min <- min(d$DECISION_DATE)
date_max <- max(d$DECISION_DATE)

# consider 'SCREENED IN AR' same as 'SCREENED IN'
for (i in 1:nrow(d)) {
  if (d$SCREENING_DECISION[i] == 'SCREENED IN AR') {
  d$SCREENING_DECISION[i] <- 'SCREENED IN'
}
}
```

This report describes `r length(unique(d$INTAKE_ID))` unique intakes with descision dates between `r date_min` and `r date_max` and `r length(unique(d$PERSON_ID))` unique alleged child victims.

```{r}
d_missing_alleg_add <- d %>% 
  group_by(INTAKE_ID) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS', 
         is.na(address)) %>% 
  select(INTAKE_ID:address_type)

d_fill_in_address <- d %>% 
  filter(INTAKE_ID %in% d_missing_alleg_add$INTAKE_ID, 
         address_type == 'CHILD_ADDRESS') %>% 
  group_by(INTAKE_ID) %>% 
  arrange(desc(ADDRESS_START)) %>% 
  slice(1) %>% 
  select(INTAKE_ID, address:dep_index)

d_missing_alleg_add <- left_join(d_missing_alleg_add, d_fill_in_address, by = 'INTAKE_ID')

d <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS' & !is.na(address) |
           address_type == 'CHILD_ADDRESS') %>% 
  bind_rows(d_missing_alleg_add) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS')
```

`r length(unique(d_missing_alleg_add$INTAKE_ID))` intakes are missing allegation address. The most recently entered child address will be used.

### Geocoding Summary

```{r}
intake_geocode_summary <- d %>% 
  filter(!duplicated(INTAKE_ID)) %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))

child_geocode_summary <- d %>% 
  filter(!duplicated(PERSON_ID)) %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))

rbind(intake_geocode_summary, child_geocode_summary) %>% 
  filter(`is.na(lat)` == FALSE) %>% 
  mutate(Level = c('Intake', 'ACV'), 
         `N` = c(length(unique(d$INTAKE_ID)), length(unique(d$PERSON_ID))),
         `N (%) Geocoded` = paste0(n, " (", pct, "%)")) %>% 
  select(Level, `N`, `N (%) Geocoded`)
```

### Deprivation Index by Screening Decision Summary

Intakes

```{r}
intake_dep_summary <- d %>% 
  filter(!duplicated(INTAKE_ID), 
         !is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% 
  summarize(mean_dep = round(mean(dep_index, na.rm = T),2), 
            sd_dep = round(sd(dep_index, na.rm = T), 1))

d %>% 
  filter(!duplicated(INTAKE_ID), 
         !is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1),
         `N (%)` = glue::glue('{n} ({pct}%)')) %>% 
  left_join(intake_dep_summary, by = 'SCREENING_DECISION') %>% 
  mutate(mean_sd = glue::glue('{mean_dep} ({sd_dep})')) %>% 
  select(Decision = SCREENING_DECISION, `N (%)`, `Deprivation Index Mean (sd) ` = mean_sd)
```

ACV 

```{r}
child_dep_summary <- d %>% 
  filter(!duplicated(PERSON_ID), 
         !is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% 
  summarize(mean_dep = round(mean(dep_index, na.rm = T),2), 
            sd_dep = round(sd(dep_index, na.rm = T), 1))

d %>% 
  filter(!duplicated(PERSON_ID),
         !is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1),
         `N (%)` = glue::glue('{n} ({pct}%)')) %>% 
  left_join(child_dep_summary, by = 'SCREENING_DECISION') %>% 
  mutate(mean_sd = glue::glue('{mean_dep} ({sd_dep})')) %>% 
  select(Decision = SCREENING_DECISION, `N (%)`, `Deprivation Index Mean (sd) ` = mean_sd)
```

### Mandated Reporter Summary

```{r}
d_mandated <- d %>% 
  filter(MANDATED_REPORTER == 'Yes')

d_mandated_intakes <- unique(d_mandated$INTAKE_ID)

d <- d %>% 
  mutate(at_least_one_mandated_reporter = ifelse(INTAKE_ID %in% d_mandated_intakes, 'yes', 'no'))
```

`r length(d_mandated_intakes)` (`r round(length(d_mandated_intakes)/length(unique(d$INTAKE_ID))*100,1)`%) intakes were reported by at least one mandated reporter.

```{r}
d %>% 
  filter(!duplicated(INTAKE_ID), 
         !is.na(lat)) %>% 
  group_by(at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1),
         `N (%)` = glue::glue('{n} ({pct}%)')) %>% 
  select(`At Least One Mandated Reporter` = at_least_one_mandated_reporter, 
         Decision = SCREENING_DECISION, `N (%)`)
```


# Neighborhood Summary

```{r}
tract_to_neighborhood <- readRDS('/app/tract_to_neighborhood.rds')

d_neigh_intake <- d  %>%
  filter(!duplicated(INTAKE_ID)) %>% 
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood) %>% 
  summarize(n_intakes = n())

intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_intakes_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(intakes_neighborhood, by = 'neighborhood')

##
mr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_mandated_reporter_intakes = n()) %>% 
  filter(at_least_one_mandated_reporter == 'yes') %>% 
  ungroup() %>% 
  select(-at_least_one_mandated_reporter)

mr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(at_least_one_mandated_reporter == 'yes', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_mandated_reporter_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_mandated_reporter_intakes_screened_in) %>% 
  left_join(mr_intakes_neighborhood, by = 'neighborhood')

##

nmr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_nonmandated_reporter_intakes = n()) %>% 
  filter(at_least_one_mandated_reporter == 'no') %>% 
  ungroup() %>% 
  select(-at_least_one_mandated_reporter)

nmr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(at_least_one_mandated_reporter == 'no', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_nonmandated_reporter_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_nonmandated_reporter_intakes_screened_in) %>% 
  left_join(nmr_intakes_neighborhood, by = 'neighborhood')

##
d_neigh_child <- d  %>%
  filter(!duplicated(PERSON_ID)) %>% 
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

child_neighborhood <- d_neigh_child %>% 
  group_by(neighborhood) %>% 
  summarize(n_children = n())

child_screen_neighborhood <- d_neigh_child %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_children_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(child_neighborhood, by = 'neighborhood')

d_neighborhood <- intake_screen_neighborhood %>% 
  left_join(child_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(mr_intake_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(nmr_intake_screen_neighborhood, by = 'neighborhood')

neighborhood_shp <- readRDS('/app/ham_neighborhoods_dep_index_shp.rds')

d_neighborhood <- neighborhood_shp %>% 
  left_join(d_neighborhood, by = 'neighborhood') %>% 
  mutate_at(vars(n_intakes, n_intakes_screened_in, 
                 n_children, n_children_screened_in,
                 n_mandated_reporter_intakes, n_mandated_reporter_intakes_screened_in), 
            ~ifelse(.x < 10, NA, .x)) %>% 
  mutate(n_intakes_per_1000hh = n_intakes/num_hh*1000,
         n_intakes_screened_in_per_1000hh = n_intakes_screened_in/num_hh*1000,
         intake_fractional_screen_in = n_intakes_screened_in_per_1000hh/n_intakes_per_1000hh,
         n_children_per_1000 = n_children/pop_under_18*1000,
         n_children_screened_in_per_1000 = n_children_screened_in/pop_under_18*1000,
         child_fractional_screen_in = n_children_screened_in_per_1000/n_children_per_1000,
         n_intakes_by_mandated_reporter_per_1000hh = n_mandated_reporter_intakes/num_hh*1000,
         n_intakes_by_mandated_reporter_screened_in_per_1000hh = n_mandated_reporter_intakes_screened_in/num_hh*1000,
         intake_by_mandated_reporter_fractional_screen_in = 
         n_intakes_by_mandated_reporter_screened_in_per_1000hh/n_intakes_by_mandated_reporter_per_1000hh,
         n_intakes_by_nonmandated_reporter_per_1000hh = n_nonmandated_reporter_intakes/num_hh*1000,
         n_intakes_by_nonmandated_reporter_screened_in_per_1000hh = n_nonmandated_reporter_intakes_screened_in/num_hh*1000,
         intake_by_nonmandated_reporter_fractional_screen_in = 
           n_intakes_by_nonmandated_reporter_screened_in_per_1000hh/n_intakes_by_nonmandated_reporter_per_1000hh) %>%
  mutate_if(is.numeric, ~round(.x, digits = 2))
  
d_neighborhood %>%
  st_drop_geometry() %>% 
  select(Neighborhood = neighborhood, 
         `Deprivation Index` = dep_index,
        `Number of Intakes` = n_intakes, 
        `Intakes Screened In` = n_intakes_screened_in,
        `Number of Households` = num_hh, 
        `Intake Rate` = n_intakes_per_1000hh,
        `Intake Screen-In Rate` = n_intakes_screened_in_per_1000hh,
        `Screen-In/Intake` = intake_fractional_screen_in,
        `Number of ACV` = n_children, 
        `Children Screened In` = n_children_screened_in, 
        `Population under 18` = pop_under_18,
        `ACV Rate` = n_children_per_1000, 
        `ACV Screen-In Rate` = n_children_screened_in_per_1000,
        `Screen-In/ACV` = child_fractional_screen_in,
        `Number of Intakes by Mandated Reporter` = n_mandated_reporter_intakes,
        `Intakes by Mandated Reporter Screened In` = n_mandated_reporter_intakes_screened_in,
        `Mandated Reporter Intake Rate` = n_intakes_by_mandated_reporter_per_1000hh,
        `Mandated Reporter Intake Screen-In Rate` = n_intakes_by_mandated_reporter_screened_in_per_1000hh,
        `Mandated Reporter Screen-In/Intake` = intake_by_mandated_reporter_fractional_screen_in,
        `Number of Intakes by Non-Mandated Reporter` = n_nonmandated_reporter_intakes,
        `Intakes by Non-Mandated Reporter Screened In` = n_nonmandated_reporter_intakes_screened_in,
        `Non-Mandated Reporter Intake Rate` = n_intakes_by_nonmandated_reporter_per_1000hh,
        `Non-Mandated Reporter Intake Screen-In Rate` = n_intakes_by_nonmandated_reporter_screened_in_per_1000hh,
        `Non-Mandated Reporter Screen-In/Intake` = intake_by_nonmandated_reporter_fractional_screen_in) %>% 
  DT::datatable()
```

## Maps by Intake

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_intakes_per_1000hh',
                      'n_intakes_screened_in_per_1000hh',
                      'intake_fractional_screen_in',
                      'dep_index'),
              title = c('Intake Rate',
                        'Intake Screen-In Rate',
                        'Screen-In/Intake',
                        'Deprivation Index'),
              popup.vars = c('Intake Rate' = 'n_intakes_per_1000hh',
                        'Intake Screen-In Rate' = 'n_intakes_screened_in_per_1000hh',
                        'Screen-In/Intake' = 'intake_fractional_screen_in',
                        'Deprivation Index' = 'dep_index'),
              alpha = 0.8,
              #palette = 'viridis'
              ) +
  tm_scale_bar() +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Maps by Intake (Mandated Reporter)

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_intakes_by_mandated_reporter_per_1000hh',
                      'n_intakes_by_mandated_reporter_screened_in_per_1000hh',
                      'intake_by_mandated_reporter_fractional_screen_in',
                      'dep_index'),
              title = c('Mandated Reporter Intake Rate',
                        'Mandated Reporter Intake Screen-In Rate',
                        'Mandated Reporter Screen-In/Intake',
                        'Deprivation Index'),
              popup.vars = c('Mandated Reporter Intake Rate' = 'n_intakes_by_mandated_reporter_per_1000hh',
                        'Mandated Reporter Intake Screen-In Rate' = 'n_intakes_by_mandated_reporter_screened_in_per_1000hh',
                        'Mandated Reporter Screen-In/Intake' = 'intake_by_mandated_reporter_fractional_screen_in',
                        'Deprivation Index' = 'dep_index'),
              alpha = 0.8,
              #palette = 'viridis'
              ) +
  tm_scale_bar() +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Maps by Intake (Non-Mandated Reporter)

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_intakes_by_nonmandated_reporter_per_1000hh',
                      'n_intakes_by_nonmandated_reporter_screened_in_per_1000hh',
                      'intake_by_nonmandated_reporter_fractional_screen_in',
                      'dep_index'),
              title = c('Non-Mandated Reporter Intake Rate',
                        'Non-Mandated Reporter Intake Screen-In Rate',
                        'Non-Mandated Reporter Screen-In/Intake',
                        'Deprivation Index'),
              popup.vars = c('Non-Mandated Reporter Intake Rate' = 'n_intakes_by_nonmandated_reporter_per_1000hh',
                        'Non-Mandated Reporter Intake Screen-In Rate' = 'n_intakes_by_nonmandated_reporter_screened_in_per_1000hh',
                        'Non-Mandated Reporter Screen-In/Intake' = 'intake_by_nonmandated_reporter_fractional_screen_in',
                        'Deprivation Index' = 'dep_index'),
              alpha = 0.8,
              #palette = 'viridis'
              ) +
  tm_scale_bar() +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Maps by Alleged Child Victim

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_children_per_1000',
                      'n_children_screened_in_per_1000',
                      'child_fractional_screen_in',
                      'dep_index'),
              title = c('ACV Rate',
                        'ACV Screen-In Rate',
                        'Screen-In/ACV',
                        'Deprivation Index'),
              popup.vars = c('ACV Rate' = 'n_children_per_1000',
                        'ACV Screen-In Rate' = 'n_children_screened_in_per_1000',
                        'Screen-In/ACV' = 'child_fractional_screen_in',
                        'Deprivation Index' = 'dep_index'),
              alpha = 0.8,
             # palette = 'viridis'
             ) +
  tm_scale_bar() +
  tm_layout(frame = FALSE,
            asp = 4)
```
