---
title: "Intakes by Mandated Reporter Neighborhood-Level Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: kable
params: 
  d: d
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(knitr)
library(tmap)
tmap_mode('view')
```

```{r, eval = F}
d <- params$d
tract_to_neighborhood <- readRDS('/app/tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('/app/ham_neighborhoods_dep_index_shp.rds')
```

```{r, eval = T}
d <- read_csv('test/simulated_jfs_data_geocoded.csv',
              col_types = cols(INTAKE_ID = col_character(),
                               SCREENING_DECISION = col_character(),
                               DECISION_DATE = col_date(),
                               PERSON_ID = col_character(),
                               RACE = col_character(),
                               ADDRESS_START = col_date(),
                               MANDATED_REPORTER = col_character(),
                               REPORTER_PERSON_ID = col_character(),
                               PROVIDER_ID = col_character(),
                               PROVIDER_NAME = col_character(),
                               address_type = col_character(),
                               address = col_character(),
                               bad_address = col_logical(),
                               PO = col_logical(),
                               lat = col_double(),
                               lon = col_double(),
                               score = col_double(),
                               precision = col_character(),
                               precise_geocode = col_logical(),
                               fips_tract_id = col_character(),
                               fraction_assisted_income = col_double(),
                               fraction_high_school_edu = col_double(),
                               median_income = col_double(),
                               fraction_no_health_ins = col_double(),
                               fraction_poverty = col_double(),
                               fraction_vacant_housing = col_double(),
                               dep_index = col_double()
                               ))

tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

# Overall Summary

```{r}
date_min <- min(d$DECISION_DATE)
date_max <- max(d$DECISION_DATE)

# consider 'SCREENED IN AR' same as 'SCREENED IN'
for (i in 1:nrow(d)) {
  if (d$SCREENING_DECISION[i] == 'SCREENED IN AR') {
  d$SCREENING_DECISION[i] <- 'SCREENED IN'
}
}
```

- This report summarizes `r length(unique(d$INTAKE_ID))` intakes with descision dates between `r date_min` and `r date_max`. 

```{r}
d_missing_alleg_add <- d %>% 
  group_by(INTAKE_ID) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS', 
         is.na(address)) %>% 
  select(INTAKE_ID:address_type)

d_fill_in_address <- d %>% 
  filter(INTAKE_ID %in% d_missing_alleg_add$INTAKE_ID, 
         address_type == 'CHILD_ADDRESS') %>% 
  group_by(INTAKE_ID) %>% 
  arrange(desc(ADDRESS_START)) %>% 
  slice(1) %>% 
  select(INTAKE_ID, address:dep_index)

d_missing_alleg_add <- left_join(d_missing_alleg_add, d_fill_in_address, by = 'INTAKE_ID')

d <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS' & !is.na(address) |
           address_type == 'CHILD_ADDRESS') %>% 
  bind_rows(d_missing_alleg_add) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS')
```

- `r length(unique(d_missing_alleg_add$INTAKE_ID))` intakes are missing allegation address. The most recently entered child address will be used.

```{r}
### Geocoding Summary
d_intake <- filter(d, !duplicated(INTAKE_ID)) %>% 
  select(-PERSON_ID, -RACE, -ADDRESS_START, -REPORTER_PERSON_ID,
         -address_type)

intake_geocode_summary <- d_intake %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))
```

- `r intake_geocode_summary$n[2]` (`r intake_geocode_summary$pct[2]`%) intakes had an address that was not able to be geocoded.

```{r}
### Mandated Reporter Summary
d_mandated <- d %>% 
  filter(MANDATED_REPORTER == 'Yes')

d_mandated_intakes <- unique(d_mandated$INTAKE_ID)

d_intake <- d_intake %>% 
  mutate(at_least_one_mandated_reporter = ifelse(INTAKE_ID %in% d_mandated_intakes, 'yes', 'no'))
```

- Some intakes have more than one reporter listed. Here, an intake is considered to reported by a mandated reporter if at least one reporter listed is a mandated reporter. `r length(d_mandated_intakes)` (`r round(length(d_mandated_intakes)/length(unique(d$INTAKE_ID))*100,1)`%) intakes were reported by at least one mandated reporter.

```{r}
mr_summary <- d_intake %>% 
  filter(!is.na(lat)) %>% 
  group_by(at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(`At Least One Mandated Reporter` = at_least_one_mandated_reporter, 
         Decision = SCREENING_DECISION, n, pct)
```

- `r mr_summary$n[3]` (`r mr_summary$pct[3]`%) intakes reported by a **mandated reporter** were **screened in**. `r mr_summary$n[4]` (`r mr_summary$pct[4]`%) intakes reported by a **mandated reporter** were **screened out**.

- `r mr_summary$n[1]` (`r mr_summary$pct[1]`%) intakes reported by a **non-mandated reporter** were **screened in**. `r mr_summary$n[2]` (`r mr_summary$pct[2]`%) intakes reported by a **non-mandated reporter** were **screened out**.

# Neighborhood Summary

The table below summarizes intakes, screening decision, mandated reporter status, and demographic information by neighborhood. The table can be sorted by clicking on the column name or searched using the search box. 

```{r}
d_neigh_intake <- d_intake  %>%
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood) %>% 
  summarize(n_intakes = n())

intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_intakes_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(intakes_neighborhood, by = 'neighborhood')

##
mr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_mandated_reporter_intakes = n()) %>% 
  filter(at_least_one_mandated_reporter == 'yes') %>% 
  ungroup() %>% 
  select(-at_least_one_mandated_reporter)

mr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(at_least_one_mandated_reporter == 'yes', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_mandated_reporter_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_mandated_reporter_intakes_screened_in) %>% 
  left_join(mr_intakes_neighborhood, by = 'neighborhood')

##

nmr_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter) %>% 
  summarize(n_nonmandated_reporter_intakes = n()) %>% 
  filter(at_least_one_mandated_reporter == 'no') %>% 
  ungroup() %>% 
  select(-at_least_one_mandated_reporter)

nmr_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, at_least_one_mandated_reporter, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(at_least_one_mandated_reporter == 'no', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_nonmandated_reporter_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_nonmandated_reporter_intakes_screened_in) %>% 
  left_join(nmr_intakes_neighborhood, by = 'neighborhood')

d_neighborhood <- intake_screen_neighborhood %>% 
  left_join(mr_intake_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(nmr_intake_screen_neighborhood, by = 'neighborhood')

d_neighborhood <- neighborhood_shp %>% 
  left_join(d_neighborhood, by = 'neighborhood') %>% 
  mutate_at(vars(n_intakes, n_intakes_screened_in, 
                 n_mandated_reporter_intakes, 
                 n_mandated_reporter_intakes_screened_in,
                 n_nonmandated_reporter_intakes, 
                 n_nonmandated_reporter_intakes_screened_in), 
            ~ifelse(.x < 5, NA, .x)) %>%  # suppress if n < 5 for privacy reasons
  mutate(n_intakes_per_1000hh = n_intakes/num_hh*1000,
         intake_fractional_screen_in = n_intakes_screened_in/n_intakes,
         n_intakes_by_mandated_reporter_per_1000hh = n_mandated_reporter_intakes/num_hh*1000,
         intake_by_mandated_reporter_fractional_screen_in = n_mandated_reporter_intakes_screened_in/n_mandated_reporter_intakes,
         n_intakes_by_nonmandated_reporter_per_1000hh = n_nonmandated_reporter_intakes/num_hh*1000,
         intake_by_nonmandated_reporter_fractional_screen_in = n_nonmandated_reporter_intakes_screened_in/n_nonmandated_reporter_intakes) %>%
  mutate_if(is.numeric, ~round(.x, digits = 2))
  
d_neighborhood %>%
  st_drop_geometry() %>% 
  select(Neighborhood = neighborhood, 
        `Number of Intakes` = n_intakes, 
        `Intakes Screened In` = n_intakes_screened_in,
        `Number of Households` = num_hh, 
        `Number Intakes per 1000 Households` = n_intakes_per_1000hh,
        `Fraction of Intakes Screened In` = intake_fractional_screen_in,
        `Number of Intakes by Mandated Reporter` = n_mandated_reporter_intakes,
        `Mandated Reporter Intakes per 1000 Households` = n_intakes_by_mandated_reporter_per_1000hh,
        `Intakes by Mandated Reporter Screened In` = n_mandated_reporter_intakes_screened_in,
        `Fraction of Mandated Reporter Intakes Screened In` = intake_by_mandated_reporter_fractional_screen_in,
        `Number of Intakes by Non-Mandated Reporter` = n_nonmandated_reporter_intakes,
        `Non-Mandated Reporter Intakes per 1000 Households` = n_intakes_by_nonmandated_reporter_per_1000hh,
        `Intakes by Non-Mandated Reporter Screened In` = n_nonmandated_reporter_intakes_screened_in,
        `Fraction of Non-Mandated Reporter Intakes Screened In` = intake_by_nonmandated_reporter_fractional_screen_in,
        `Deprivation Index` = dep_index) %>% 
  DT::datatable()
```

## Neighborhood Maps

The maps below are interactive and can be panned and zoomed. Clicking on a neighborhood will provide a pop-up with more information about that neighborhood.

### Intakes per 1000 Households

The two maps below show the Intake Rate (number of intakes per 1000 households) by neighborhood and by mandated reporter status.  

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_intakes_by_mandated_reporter_per_1000hh',
                      'n_intakes_by_nonmandated_reporter_per_1000hh'),
              title = c('Mandated Reporter',
                        'Non-Mandated Reporter'),
              popup.vars = c('Mandated Reporter Intakes per 1000 Households' = 'n_intakes_by_mandated_reporter_per_1000hh',
                             'Non-Mandated Reporter Intakes per 1000 Households' = 'n_intakes_by_nonmandated_reporter_per_1000hh'),
              alpha = 0.8,
              palette = 'Blues') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

### Fraction of Intakes Screened In

The two maps below show the Fraction of Intakes Screened In (number of intakes that were screened in / number of intakes) by neighborhood and by mandated reporter status. 

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('intake_by_mandated_reporter_fractional_screen_in',
                      'intake_by_nonmandated_reporter_fractional_screen_in'),
              title = c('Mandated Reporter',
                        'Non-Mandated Reporter'),
              popup.vars = c('Fraction Mandated Reporter Intakes Screened In' = 'intake_by_mandated_reporter_fractional_screen_in',
                        'Fraction Non-Mandated Reporter Intakes Screened In' = 'intake_by_nonmandated_reporter_fractional_screen_in'),
              alpha = 0.8,
              palette = 'Oranges') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Percent Intakes Screened In Over Time

**add description/interpretation of charts from Stuart & team**

```{r fig.width=10}
source("p_general_join.R", local = knitr::knit_global())
date_agg <- 'week'

screen_shifts <- tribble(
  ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(CENTERLINE_START=ymd(CENTERLINE_START),
         CENTERLINE_END=ymd(CENTERLINE_END),
         IN_CALC=TRUE)

screen_data <- d_intake %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

screen_centers <- p_chart_centerlines(data = screen_data,
                              date_name = 'REPORT_WEEK',
                              factor = c('MEASURE'),
                              shifts = screen_shifts,
                              base_start_date = ymd(date_min),
                              base_end_date = ymd(date_max),
                              numer = 'NUM',
                              denom = 'DENOM',
                              time_period = date_agg)

cc_screened_in <- control_chart_plot(screen_centers, 
                                     x_axis = REPORT_WEEK, 
                                     y_axis = RATE) +
  ggtitle('Screen In Rate')
cc_screened_in
```

```{r fig.width=10}
d_intake <- rename(d_intake, MANDATED_REPORTER_STATUS = at_least_one_mandated_reporter) %>% 
  mutate(MANDATED_REPORTER_STATUS = ifelse(MANDATED_REPORTER_STATUS == 'yes', 'Mandated Reporter', 'Non-Mandated Reporter'))

mr_sreen_shifts <- tribble(
  ~MANDATED_REPORTER_STATUS, ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(CENTERLINE_START = ymd(CENTERLINE_START),
         CENTERLINE_END = ymd(CENTERLINE_END),
         IN_CALC = TRUE)

mr_screen_data <- d_intake %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(MANDATED_REPORTER_STATUS, REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

mr_centers <- p_chart_centerlines(data = mr_screen_data,
                                  date_name = 'REPORT_WEEK',
                                  factor = c('MANDATED_REPORTER_STATUS','MEASURE'),
                                  shifts = mr_sreen_shifts,
                                  base_start_date = ymd(date_min),
                                  base_end_date = ymd(date_max),
                                  numer = 'NUM',
                                  denom = 'DENOM',
                                  time_period = date_agg)

mr_screened_in <- control_chart_plot(mr_centers,
                                     x_axis = REPORT_WEEK,
                                     y_axis = RATE) +
  facet_grid(~MANDATED_REPORTER_STATUS, scales = 'free', switch = 'y') +
  ggtitle('Screen In Rate by Mandated Reporter Status') +
  theme(strip.placement.y = 'outside',
        strip.text.y.left = element_text(angle=0))
mr_screened_in
```

