---
title: "Intakes by Race Neighborhood-Level Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: kable
params: 
  d: d
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(knitr)
library(tmap)
tmap_mode('view')
```

```{r, eval = F}
d <- params$d
tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

```{r, eval = T}
d <- read_csv('test/simulated_jfs_data_geocoded.csv',
              col_types = cols(INTAKE_ID = col_character(),
                               SCREENING_DECISION = col_character(),
                               DECISION_DATE = col_date(),
                               PERSON_ID = col_character(),
                               RACE = col_character(),
                               ADDRESS_START = col_date(),
                               MANDATED_REPORTER = col_character(),
                               REPORTER_PERSON_ID = col_character(),
                               PROVIDER_ID = col_character(),
                               PROVIDER_NAME = col_character(),
                               address_type = col_character(),
                               address = col_character(),
                               bad_address = col_logical(),
                               PO = col_logical(),
                               lat = col_double(),
                               lon = col_double(),
                               score = col_double(),
                               precision = col_character(),
                               precise_geocode = col_logical(),
                               fips_tract_id = col_character(),
                               fraction_assisted_income = col_double(),
                               fraction_high_school_edu = col_double(),
                               median_income = col_double(),
                               fraction_no_health_ins = col_double(),
                               fraction_poverty = col_double(),
                               fraction_vacant_housing = col_double(),
                               dep_index = col_double()
                               ))

tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

# Overall Summary

```{r}
date_min <- min(d$DECISION_DATE)
date_max <- max(d$DECISION_DATE)

# consider 'SCREENED IN AR' same as 'SCREENED IN'
for (i in 1:nrow(d)) {
  if (d$SCREENING_DECISION[i] == 'SCREENED IN AR') {
  d$SCREENING_DECISION[i] <- 'SCREENED IN'
}
}
```

- This report summarizes `r length(unique(d$INTAKE_ID))` intakes with descision dates between `r date_min` and `r date_max`. 

```{r}
d_missing_alleg_add <- d %>% 
  group_by(INTAKE_ID) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS', 
         is.na(address)) %>% 
  select(INTAKE_ID:address_type)

d_fill_in_address <- d %>% 
  filter(INTAKE_ID %in% d_missing_alleg_add$INTAKE_ID, 
         address_type == 'CHILD_ADDRESS') %>% 
  group_by(INTAKE_ID) %>% 
  arrange(desc(ADDRESS_START)) %>% 
  slice(1) %>% 
  select(INTAKE_ID, address:dep_index)

d_missing_alleg_add <- left_join(d_missing_alleg_add, d_fill_in_address, by = 'INTAKE_ID')

d <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS' & !is.na(address) |
           address_type == 'CHILD_ADDRESS') %>% 
  bind_rows(d_missing_alleg_add) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS')
```

- `r length(unique(d_missing_alleg_add$INTAKE_ID))` intakes are missing allegation address. The most recently entered child address will be used.

```{r}
### Geocoding Summary
d_intake <- filter(d, !duplicated(INTAKE_ID)) %>% 
  select(-PERSON_ID, -ADDRESS_START, -REPORTER_PERSON_ID,
         -address_type)

intake_geocode_summary <- d_intake %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))
```

- `r intake_geocode_summary$n[2]` (`r intake_geocode_summary$pct[2]`%) intakes had an address that was not able to be geocoded.

```{r}
### Race Reporter Summary
d_bw <- d %>% 
  filter(RACE %in% c('White', 'Black/African American'))

'%notin%'<-Negate('%in%')
d_other<-d %>%
  filter(RACE %notin% c('White', 'Black/African American'))

d_intake_other <- d_intake %>%
  filter(RACE %notin% c("White", "Black/African American"))

d_intake <- d_intake %>%
  filter(RACE %in% c("White", "Black/African American")) #Only looking at black vs white

```


```{r}
race_summary <- d_intake %>% 
  filter(!is.na(lat)) %>% 
  group_by(RACE, SCREENING_DECISION) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(RACE, Decision = SCREENING_DECISION, n, pct)

race_summary_other <- d_intake_other %>% 
  filter(!is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% #group by race first to see each indiv race breakdown
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(Decision = SCREENING_DECISION, n, pct)

```

- `r race_summary$n[3]` (`r race_summary$pct[3]`%) intakes of a **White ACV**  were **screened in**. `r race_summary$n[4]` (`r race_summary$pct[4]`%) intakes of a **White ACV** were **screened out**.

- `r race_summary$n[1]` (`r race_summary$pct[1]`%) intakes of a  **Black/African American ACV** were **screened in**. `r race_summary$n[2]` (`r race_summary$pct[2]`%) intakes of a **Black/African American ACV** were **screened out**.

- There were `r nrow(d_intake_other)` intakes of **neither** a White nor Black/African American ACV.

- `r race_summary_other$n[1]` (`r race_summary_other$pct[1]`%) intakes of a **Non-White nor Black/African American ACV**  were **screened in**. `r race_summary_other$n[2]` (`r race_summary_other$pct[2]`%) intakes of a **Non-White nor Black/African American ACV** were **screened out**.

# Neighborhood Summary

The table below summarizes intakes, screening decision, mandated reporter status, and demographic information by neighborhood. The table can be sorted by clicking on the column name or searched using the search box. 

```{r}
d_neigh_intake <- d_intake  %>%
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood) %>% 
  summarize(n_intakes = n())

intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_intakes_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(intakes_neighborhood, by = 'neighborhood')

##
white_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, RACE) %>% 
  summarize(n_white_intakes = n()) %>% 
  filter(RACE == 'White') %>% 
  ungroup() %>% 
  select(-RACE)

white_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, RACE, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(RACE == 'White', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_white_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_white_intakes_screened_in) %>% 
  left_join(white_intakes_neighborhood, by = 'neighborhood')

##

black_intakes_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, RACE) %>% 
  summarize(n_black_intakes = n()) %>% 
  filter(RACE == 'Black/African American') %>% 
  ungroup() %>% 
  select(-RACE)

black_intake_screen_neighborhood <- d_neigh_intake %>% 
  group_by(neighborhood, RACE, SCREENING_DECISION) %>% 
  tally() %>% 
  filter(RACE == 'Black/African American', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_black_intakes_screened_in = n) %>% 
  ungroup() %>% 
  select(neighborhood, n_black_intakes_screened_in) %>% 
  left_join(black_intakes_neighborhood, by = 'neighborhood')

d_neighborhood <- intake_screen_neighborhood %>% 
  left_join(white_intake_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(black_intake_screen_neighborhood, by = 'neighborhood')

d_neighborhood <- neighborhood_shp %>% 
  left_join(d_neighborhood, by = 'neighborhood') %>% 
  mutate_at(vars(n_intakes, n_intakes_screened_in, 
                 n_white_intakes, 
                 n_white_intakes_screened_in,
                 n_black_intakes, 
                 n_black_intakes_screened_in), 
            ~ifelse(.x < 10, NA, .x)) %>%  # suppress if n < 10 for privacy reasons
  mutate(n_intakes_per_1000hh = n_intakes/num_hh*1000,
         intake_fractional_screen_in = n_intakes_screened_in/n_intakes,
         n_intakes_white_per_1000hh = n_white_intakes/num_hh*1000,
         intake_white_fractional_screen_in = n_white_intakes_screened_in/n_white_intakes,
         n_intakes_black_per_1000hh = n_black_intakes/num_hh*1000,
         intake_black_fractional_screen_in = n_black_intakes_screened_in/n_black_intakes) %>%
  mutate_if(is.numeric, ~round(.x, digits = 2))
  
d_neighborhood %>%
  st_drop_geometry() %>% 
  select(Neighborhood = neighborhood, 
        `Number of Intakes` = n_intakes, 
        `Intakes Screened In` = n_intakes_screened_in,
        `Number of Households` = num_hh, 
        `Number Intakes per 1000 Households` = n_intakes_per_1000hh,
        `Fraction of Intakes Screened In` = intake_fractional_screen_in,
        `Number of White Intakes` = n_white_intakes,
        `White Intakes per 1000 Households` = n_intakes_white_per_1000hh,
        `White Intakes Screened In` = n_white_intakes_screened_in,
        `Fraction of White Intakes Screened In` = intake_white_fractional_screen_in,
        `Number of Black/African American Intakes` = n_black_intakes,
        `Black/African American Intakes per 1000 Households` = n_intakes_black_per_1000hh,
        `Black/African American Intakes Screened In` = n_black_intakes_screened_in,
        `Fraction of Black/African American Intakes Screened In` = intake_black_fractional_screen_in,
        `Deprivation Index` = dep_index) %>% 
  DT::datatable()
```

## Neighborhood Maps

The maps below are interactive and can be panned and zoomed. Clicking on a neighborhood will provide a pop-up with more information about that neighborhood.

### Intakes per 1000 Households

The two maps below show the Intake Rate (number of intakes per 1000 households) by neighborhood and by race.  

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_intakes_white_per_1000hh',
                      'n_intakes_black_per_1000hh'),
              title = c('White',
                        'Black/African American'),
              popup.vars = c('White Intakes per 1000 Households' = 'n_intakes_white_per_1000hh',
                             'Black/African American Intakes per 1000 Households' = 'n_intakes_black_per_1000hh'),
              alpha = 0.8,
              palette = 'Blues') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

### Fraction of Intakes Screened In

The two maps below show the Fraction of Intakes Screened In (number of intakes that were screened in / number of intakes) by neighborhood and by race. 

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('intake_white_fractional_screen_in',
                      'intake_black_fractional_screen_in'),
              title = c('White',
                        'Black/African American'),
              popup.vars = c('Fraction White Intakes Screened In' = 'intake_white_fractional_screen_in',
                        'Fraction Black/African American Intakes Screened In' = 'intake_black_fractional_screen_in'),
              alpha = 0.8,
              palette = 'Oranges') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Percent Intakes Screened In Over Time

**add description/interpretation of charts from Stuart & team**

```{r}
source("p_general_join.R", local = knitr::knit_global())
date_agg <- 'week'

screen_shifts <- tribble(
  ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(CENTERLINE_START=ymd(CENTERLINE_START),
         CENTERLINE_END=ymd(CENTERLINE_END),
         IN_CALC=TRUE)

screen_data <- d_intake %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

screen_centers <- p_chart_centerlines(data = screen_data,
                              date_name = 'REPORT_WEEK',
                              factor = c('MEASURE'),
                              shifts = screen_shifts,
                              base_start_date = ymd(date_min),
                              base_end_date = ymd(date_max),
                              numer = 'NUM',
                              denom = 'DENOM',
                              time_period = date_agg)

cc_screened_in <- control_chart_plot(screen_centers, 
                                     x_axis = REPORT_WEEK, 
                                     y_axis = RATE) +
  ggtitle('Screen In Rate')
cc_screened_in
```

```{r}
race_sreen_shifts <- tribble(
  ~RACE, ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(CENTERLINE_START = ymd(CENTERLINE_START),
         CENTERLINE_END = ymd(CENTERLINE_END),
         IN_CALC = TRUE)

race_screen_data <- d_intake %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(RACE, REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

race_centers <- p_chart_centerlines(data = race_screen_data,
                                  date_name = 'REPORT_WEEK',
                                  factor = c('RACE','MEASURE'),
                                  shifts = race_sreen_shifts,
                                  base_start_date = ymd(date_min),
                                  base_end_date = ymd(date_max),
                                  numer = 'NUM',
                                  denom = 'DENOM',
                                  time_period = date_agg)

race_screened_in <- control_chart_plot(race_centers,
                                     x_axis = REPORT_WEEK,
                                     y_axis = RATE) +
  facet_grid(~RACE, scales = 'free', switch = 'y') +
  ggtitle('Screen In Rate by Race') +
  theme(strip.placement.y = 'outside',
        strip.text.y.left = element_text(angle=0))
race_screened_in
```

