---
title: "Alleged Child Victims by Race Neighborhood-Level Report"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    df_print: kable
params: 
  d: d
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(knitr)
library(tmap)
tmap_mode('view')
```

```{r, eval = T}
d <- params$d
tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

```{r, eval = F}
d <- read_csv('test/simulated_jfs_data_geocoded.csv',
              col_types = cols(INTAKE_ID = col_character(),
                               SCREENING_DECISION = col_character(),
                               DECISION_DATE = col_date(),
                               PERSON_ID = col_character(),
                               RACE = col_character(),
                               ADDRESS_START = col_date(),
                               MANDATED_REPORTER = col_character(),
                               REPORTER_PERSON_ID = col_character(),
                               PROVIDER_ID = col_character(),
                               PROVIDER_NAME = col_character(),
                               address_type = col_character(),
                               address = col_character(),
                               bad_address = col_logical(),
                               PO = col_logical(),
                               lat = col_double(),
                               lon = col_double(),
                               score = col_double(),
                               precision = col_character(),
                               precise_geocode = col_logical(),
                               fips_tract_id = col_character(),
                               fraction_assisted_income = col_double(),
                               fraction_high_school_edu = col_double(),
                               median_income = col_double(),
                               fraction_no_health_ins = col_double(),
                               fraction_poverty = col_double(),
                               fraction_vacant_housing = col_double(),
                               dep_index = col_double()
                               ))

tract_to_neighborhood <- readRDS('tract_to_neighborhood.rds')
neighborhood_shp <- readRDS('ham_neighborhoods_dep_index_shp.rds')
```

# Overall Summary

```{r}
date_min <- min(d$DECISION_DATE)
date_max <- max(d$DECISION_DATE)

# consider 'SCREENED IN AR' same as 'SCREENED IN'
for (i in 1:nrow(d)) {
  if (d$SCREENING_DECISION[i] == 'SCREENED IN AR') {
  d$SCREENING_DECISION[i] <- 'SCREENED IN'
}
}
```

- This report summarizes `r length(unique(d$PERSON_ID))` ACVs with decision dates between `r date_min` and `r date_max`. 

```{r eval=T}
d_missing_alleg_add <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS', 
         is.na(address)) %>% 
  select(PERSON_ID:address_type)

d_fill_in_address <- d %>% 
  filter(PERSON_ID %in% d_missing_alleg_add$PERSON_ID, 
         address_type == 'CHILD_ADDRESS') %>% 
  group_by(PERSON_ID) %>% 
  arrange(desc(ADDRESS_START)) %>% 
  slice(1) %>% 
  select(INTAKE_ID, address:dep_index)

d_missing_alleg_add <- left_join(d_missing_alleg_add, d_fill_in_address, by = 'PERSON_ID')

d <- d %>% 
  filter(address_type == 'ALLEGATION_ADDRESS' & !is.na(address) |
           address_type == 'CHILD_ADDRESS') %>% 
  bind_rows(d_missing_alleg_add) %>% 
  filter(address_type == 'ALLEGATION_ADDRESS')
```


```{r}
### Geocoding Summary
d_acv<- filter(d, !duplicated(PERSON_ID)) %>% 
  select( -ADDRESS_START, -REPORTER_PERSON_ID,
         -address_type)

acv_geocode_summary <- d_acv %>% 
  group_by(is.na(lat)) %>% 
  tally() %>% 
  mutate(pct = round(n/sum(n)*100,1))
```

- `r acv_geocode_summary$n[2]` (`r acv_geocode_summary$pct[2]`%) ACVs had an address that was not able to be geocoded.

```{r}
### Race Reporter Summary

'%notin%'<-Negate('%in%')

d_acv_other <- d_acv %>%
  filter(RACE %notin% c("White", "Black/African American"))

d_acv <- d_acv %>%
  filter(RACE %in% c("White", "Black/African American")) #Only looking at black vs white

```


```{r}
race_summary <- d_acv %>% 
  filter(!is.na(lat)) %>% 
  group_by(RACE, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(RACE, Decision = SCREENING_DECISION, n, pct)

race_summary_other <- d_acv_other %>% 
  filter(!is.na(lat)) %>% 
  group_by(SCREENING_DECISION) %>% #group by race first to see each indiv race breakdown
  tally() %>% 
  ungroup() %>% 
  mutate(pct = round(n/sum(n)*100,1)) %>% 
  select(Decision = SCREENING_DECISION, n, pct)

```

- `r race_summary$n[4]` (`r race_summary$pct[4]`%)  **White ACVs**  were **screened in**. `r race_summary$n[5]` (`r race_summary$pct[5]`%) **White ACVs** were **screened out**.

- `r race_summary$n[1]` (`r race_summary$pct[1]`%) **Black/African American ACVs** were **screened in**. `r race_summary$n[2]` (`r race_summary$pct[2]`%) **Black/African American ACVs** were **screened out**.

- There were `r nrow(d_acv_other)` ACVs of **neither** White nor Black/African American race.

- `r race_summary_other$n[1]` (`r race_summary_other$pct[1]`%) **Non-White nor Black/African American ACVs**  were **screened in**. `r race_summary_other$n[2]` (`r race_summary_other$pct[2]`%) **Non-White nor Black/African American ACVs** were **screened out**.

# Neighborhood Summary

The table below summarizes ACVs, screening decision, race, and demographic information by neighborhood. The table can be sorted by clicking on the column name or searched using the search box. 

```{r}
d_neigh_acv <- d_acv  %>%
  mutate(fips_tract_id = as.character(fips_tract_id)) %>% 
  filter(!is.na(lat)) %>% 
  left_join(tract_to_neighborhood, by='fips_tract_id')

acv_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood) %>% 
  summarize(n_acvs = n())

acv_screen_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_acvs_screened_in = n) %>% 
  select(-n, -SCREENING_DECISION) %>% 
  left_join(acv_neighborhood, by = 'neighborhood')

##
white_acv_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood, RACE) %>% 
  summarize(n_white_acvs = n()) %>% 
  ungroup() %>% 
  filter(RACE == 'White') %>% 
  select(-RACE)

white_acv_screen_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood, RACE, SCREENING_DECISION) %>% 
  tally() %>% 
  ungroup() %>% 
  filter(RACE == 'White', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_white_acvs_screened_in = n) %>% 
  select(neighborhood, n_white_acvs_screened_in) %>% 
  left_join(white_acv_neighborhood, by = 'neighborhood')

##

black_acv_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood, RACE) %>% 
  summarize(n_black_acvs = n()) %>% 
  ungroup() %>% 
  filter(RACE == 'Black/African American') %>% 
  select(-RACE)

black_acv_screen_neighborhood <- d_neigh_acv %>% 
  group_by(neighborhood, RACE, SCREENING_DECISION) %>% 
  tally() %>%
  ungroup() %>% 
  filter(RACE == 'Black/African American', 
         SCREENING_DECISION == 'SCREENED IN') %>% 
  mutate(n_black_acvs_screened_in = n) %>% 
  select(neighborhood, n_black_acvs_screened_in) %>% 
  left_join(black_acv_neighborhood, by = 'neighborhood')

d_neighborhood <- acv_screen_neighborhood %>% 
  left_join(white_acv_screen_neighborhood, by = 'neighborhood') %>% 
  left_join(black_acv_screen_neighborhood, by = 'neighborhood')

d_neighborhood <- neighborhood_shp %>% 
  left_join(d_neighborhood, by = 'neighborhood') %>% 
  mutate_at(vars(n_acvs, n_acvs_screened_in, 
                 n_white_acvs, 
                 n_white_acvs_screened_in,
                 n_black_acvs, 
                 n_black_acvs_screened_in), 
            ~ifelse(.x < 10, NA, .x)) %>%  # suppress if n < 10 for privacy reasons
  mutate(n_acvs_per_1000 = n_acvs/pop_under_18*1000,
         acvs_fractional_screen_in = n_acvs_screened_in/n_acvs,
         n_acvs_white_per_1000 = n_white_acvs/pop_under_18*1000,
         acvs_white_fractional_screen_in = n_white_acvs_screened_in/n_white_acvs,
         n_acvs_black_per_1000 = n_black_acvs/pop_under_18*1000,
         acvs_black_fractional_screen_in = n_black_acvs_screened_in/n_black_acvs) %>%
  mutate_if(is.numeric, ~round(.x, digits = 2))
  
d_neighborhood %>%
  st_drop_geometry() %>% 
  select(Neighborhood = neighborhood, 
        `Number of ACVs` = n_acvs, 
        `ACVs Screened In` = n_acvs_screened_in,
        `Population Under 18` = pop_under_18, 
        `Number ACVs per 1000 Children` = n_acvs_per_1000,
        `Fraction of ACVs Screened In` = acvs_fractional_screen_in,
        `Number of White ACVs` = n_white_acvs,
        `White ACVs per 1000 Children` = n_acvs_white_per_1000,
        `White ACVs Screened In` = n_white_acvs_screened_in,
        `Fraction of White ACVs Screened In` = acvs_white_fractional_screen_in,
        `Number of Black/African American ACVs` = n_black_acvs,
        `Black/African American ACVs per 1000 Children` = n_acvs_black_per_1000,
        `Black/African American ACVs Screened In` = n_black_acvs_screened_in,
        `Fraction of Black/African American ACVs Screened In` = acvs_black_fractional_screen_in,
        `Deprivation Index` = dep_index) %>% 
  DT::datatable()
```

## Neighborhood Maps

The maps below are interactive and can be panned and zoomed. Clicking on a neighborhood will provide a pop-up with more information about that neighborhood.

### ACVs per 1000 Children

The two maps below show the ACV Rate (number of acvs per 1000 children) by neighborhood and by race.  

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('n_acvs_white_per_1000',
                      'n_acvs_black_per_1000'),
              title = c('White',
                        'Black/African American'),
              popup.vars = c('White ACVs per 1000 Children' = 'n_acvs_white_per_1000',
                             'Black/African American ACVs per 1000 Children' = 'n_acvs_black_per_1000'),
              alpha = 0.8,
              palette = 'Blues') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

### Fraction of ACVs Screened In

The two maps below show the Fraction of ACVs Screened In (number of ACVs that were screened in / number of ACVs) by neighborhood and by race. 

```{r, fig.width = 10, fig.height=8}
tm_basemap("CartoDB.Positron") +
  tm_shape(d_neighborhood) +
  tm_polygons(col = c('acvs_white_fractional_screen_in',
                      'acvs_black_fractional_screen_in'),
              title = c('White',
                        'Black/African American'),
              popup.vars = c('Fraction White ACVs Screened In' = 'acvs_white_fractional_screen_in',
                        'Fraction Black/African American ACVs Screened In' = 'acvs_black_fractional_screen_in'),
              alpha = 0.8,
              palette = 'Oranges') +
  tm_scale_bar() +
  tm_facets(ncol = 2,
            free.scales.fill = FALSE) +
  tm_layout(frame = FALSE,
            asp = 4)
```

## Percent ACVs Screened In Over Time

**add description/interpretation of charts from Stuart & team**

```{r}
source("p_general_join.R", local = knitr::knit_global())
date_agg <- 'week'

acv_screen_shifts <- tribble(
  ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(MEASURE = as.character(MEASURE), 
         CENTERLINE_START=ymd(CENTERLINE_START),
         CENTERLINE_END=ymd(CENTERLINE_END),
         IN_CALC=TRUE)

acv_screen_data <- d_acv %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  ungroup() %>% 
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

acv_screen_data<-acv_screen_data[-54,]#remove na row at end of group

acv_screen_centers <- p_chart_centerlines(data = acv_screen_data,
                              date_name = 'REPORT_WEEK',
                              factor = c('MEASURE'),
                              shifts = acv_screen_shifts,
                              base_start_date = ymd(date_min),
                              base_end_date = ymd(date_max),
                              numer = 'NUM',
                              denom = 'DENOM',
                              time_period = date_agg)

acv_screened_in <- control_chart_plot(acv_screen_centers, 
                                     x_axis = REPORT_WEEK, 
                                     y_axis = RATE) +
  ggtitle('Screen In Rate')
acv_screened_in
```

```{r}
#d_intake <- rename(d_intake, MANDATED_REPORTER_STATUS = at_least_one_mandated_reporter) %>% 
#  mutate(MANDATED_REPORTER_STATUS = ifelse(MANDATED_REPORTER_STATUS == 'yes', 'Mandated Reporter', 'Non-Mandated Reporter'))

race_sreen_shifts <- tribble(
  ~RACE, ~MEASURE, ~CENTERLINE_START, ~CENTERLINE_END) %>%
  mutate(RACE = as.character(RACE), 
         MEASURE = as.character(MEASURE),
         CENTERLINE_START = ymd(CENTERLINE_START),
         CENTERLINE_END = ymd(CENTERLINE_END),
         IN_CALC = TRUE)

race_screen_data <- d_acv %>%
  mutate(REPORT_WEEK = floor_date(DECISION_DATE, date_agg)) %>%
  group_by(RACE, REPORT_WEEK) %>%
  summarise(NUM = sum(SCREENING_DECISION == 'SCREENED IN',na.rm = TRUE),
            DENOM = n(),
            .groups = 'drop') %>%
  ungroup() %>% 
  mutate(RATE = NUM/DENOM*1.0,
         MEASURE = 'SCREENED_IN')

race_screen_data<-race_screen_data[-c(54,108),]#remove na rows at end of each group's period

race_centers <- p_chart_centerlines(data = race_screen_data,
                                  date_name = 'REPORT_WEEK',
                                  factor = c('RACE','MEASURE'),
                                  shifts = race_sreen_shifts,
                                  base_start_date = ymd(date_min),
                                  base_end_date = ymd(date_max),
                                  numer = 'NUM',
                                  denom = 'DENOM',
                                  time_period = date_agg)

race_screened_in <- control_chart_plot(race_centers,
                                     x_axis = REPORT_WEEK,
                                     y_axis = RATE) +
  facet_grid(~RACE, scales = 'free', switch = 'y') +
  ggtitle('ACV Screen In Rate by Race') +
  theme(strip.placement.y = 'outside',
        strip.text.y.left = element_text(angle=0))
race_screened_in
```

